Dynamic Topic Modeling for Voice Dialogues

### 2024-05-02 paper/main.tex
fix title and some new cites

\title{Dynamic Topic Modeling for Voice Dialogues}
\author{Miakov Timofey Ilich}
\supervisor{Professor NRU HSE - Nizhniy Novgorod}{L.V. Savchenko}
\Year{2024}
\Abstract{}

@@

The main objectives of the research work:
\begin{enumerate}
    \item Investigate existing solutions for dynamic text and dialogue topic modelling
    \item The definition of the main stages for DTM for audio dialogues
    \item The identification of suitable training data sets and their collection
    \item An exploration of the possibilities of using large language models for some stages and the selection of models suitable for training in limited resources
    \item The development of the architecture of all stages and their interconnections
    \item Selection of appropriate metrics and measurement of the quality of the approaches used at each stage
    \item Visual analysis of the pipeline operation on pre-selected audio data
\end{enumerate}

@@

Since one of the significant tasks is to use DTM for audio data, the first, but optional, stage of our pipeline will be a model for automatic speech recognition. 
In this section, we will look at the whisper model from OpenAI and the MODEL 2.

@@

%need perephrace

@@

\section{ASR experiments}

>>>>

\title{Dynamic Topic Modeling for Voice Dialogues}
\author{Miakov Timofey Ilich}
\Abstract{}

@@

The main objectives of the research work:
\begin{enumerate}
    \item Investigate existing solutions for dynamic text and dialogue topic modelling
    \item The definition of the main stages for DTM for audio dialogues
    \item The identification of suitable training data sets and their collection
    \item An exploration of the possibilities of using large language models for some stages and the selection of models suitable for training in limited resources
    \item The development of the architecture of all stages and their interconnections
    \item Selection of appropriate metrics and measurement of the quality of the approaches used at each stage
    \item Visual evaluation of the pipeline inference on choosen audio samples
\end{enumerate}

@@

Since one of the significant tasks is to use DTM for audio data, the first, but optional, stage of our pipeline will be a model for automatic speech recognition. 
In this section, we will look at the Whisper \cite{whisper:2022} model from OpenAI.

@@

@@
